Example datasets

### 2024-02-19 data.qmd
Cite beyens

library(tidyverse)
```

Throughout, we use an example dataset from "A primer on two-level dynamic structural equation models for intensive longitudinal data in Mplus" [@mcneishPrimerTwolevelDynamic2020]. Those data are available on the OSF (<https://osf.io/wuprx/>). Here we download, clean, and save the data for use in our analyses.

@@

@@

# Active, Passive, and Total were sums of the platform (e.g. whatsapp) times
d <- read_spss(path) %>% 
  mutate(
    class = factor(ClassNr),
    person = factor(EthicaID),
    # I think they divided this by ten
    time = (OccNrR - 1),
    # active = rowSums(select(., contains("Act")), na.rm = TRUE),
    sm = rowSums(select(., contains("Pas")), na.rm = TRUE) / 60,
    wb = as.numeric(AffWB) / 7, 
    .keep = "none"
  ) %>% 
  arrange(person, class, time)

# Remove times in excess of 60min (1 hour)
d <- d %>% 
  mutate(
    across(c(sm), ~if_else(. > 1, 1, .))
  )

# Centered and lagged variables
d <- d %>% 
  mutate(
    sm_b = mean(sm, na.rm = TRUE),
    sm_c = sm - mean(sm, na.rm = TRUE),
    across(
      c(wb),
      .fns = list(lag = ~lag(.))
    ),
    .by = person
  )

d

>>>>

library(haven)
library(tidyverse)
```

We will use two example datasets. The first is from "A primer on two-level dynamic structural equation models for intensive longitudinal data in Mplus" [@mcneishPrimerTwolevelDynamic2020]. Those data are available on the OSF (<https://osf.io/wuprx/>). Here we download, clean, and save the data for use in our analyses.

@@

Our second dataset, analyzed in the manuscript, is from @beyens2020. Below, we download & wrangle then save it for later analyses.

@@

# Active, Passive, and Total were sums of the platform (e.g. whatsapp) times
d <- read_spss(path) %>% 
  mutate(
    class = factor(ClassNr),
    person = factor(EthicaID),
    time = (OccNrR - 1),
    sm = rowSums(select(., contains("Pas"), contains("Pas")), na.rm = TRUE) / 60,
    happy = as.numeric(AffWB) / 7, 
    .keep = "none"
  ) %>% 
  arrange(person, class, time)

# Sum scores exceeding 60minutes (i.e., less than 2.5% of all occasions per subscale) were recoded to 60 minutes. (Beyens et al. p.9)
d$sm <- if_else(d$sm > 1.0, 1.0, d$sm)

# Lag well-being
d <- d %>% 
  mutate(
    happy_lag = lag(happy),
    .by = person
  )
